---
title: "Programming Background"
author: "Grace Holliday"
date: "2023-06-05"
output: github_document
---

```{r setup, include=FALSE}
library('rmarkdown')
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path = "../images/")
## render("C:/Users/Sarah/Documents/ghollid.github.io/_Rmd/2023-06-04-Programming-Background.Rmd",output_format="github_document",output_dir="../_posts/",output_options=list(keep_html=FALSE)) ## 

```

## My programming background:

The other programming software I have primarily used is SAS.  My thoughts on R 
as compared to SAS are that I have more experience with R (given previous
experiences prior to the course), so I tend to lean on it more often than not.
That being said, I do currently work in statistical programming where we use 
SAS for everything!  I think that R is much more user friendly than SAS and 
other languages and I appreciated that when I first learned it.  I think I 
would have had a harder time learning SAS had I not learned R (or some other
software like MATLab (not my favorite haha)) first.  I enjoy the object-
oriented functionality in R.  I often find myself writing SAS code and thinking
"I know exactly how I would do this if I was only using R!" and I think that is
a huge factor in that.  I like that it is open-source and free, and that there
is likely a package out there for almost anything you can think of.  I do miss
that SAS is not case sensitive!  Switching between the two I constantly find 
myself calling functions or packages that don't exist in R because of some
difference in the casing I used to call it.  I definitely don't consider R as a
difficult language to learn.  It's very easy to pick up on and find resources/
communities online that will be helpful if you need it.  My experience first 
learning R came in an undergraduate research lab at Clemson University.  As an
interdisciplinary biology lab, R is primarily used for any analyses they may 
need to run and I was taught on a bit of a 'need-to-know' basis and eventually
became independent enough in R that I could manage almost anything on my own. 
It was an extremely valuable experience and has allowed me to succeed not only 
in this class so far, but in my own research collaborations.

## Example R Markdown Output

```{r, echo=TRUE}
plot(iris)
```



